---
title: "Detecting coordinated posting behaviour with coorsim"
format:
  html: default
---

```{r}
#| include: false
set.seed(42)
```

## Learning Objectives

By the end of this tutorial, you will be able to

1. find similar posts published within a short time window,
2. group accounts into communities and plot them,
3. describe communities with an LLM,
4. report the share of flagged posts and accounts.

## Target audience

This tutorial is aimed at beginners with some knowledge of R.

## Setting up the computational environment

Install the R packages.

```{r}
#| label: install-packages
#| eval: false
install.packages("remotes")
remotes::install_github("thieled/coorsim@231617d405890341eed652037088e1136e696f47")
```

And load the R packages.

```{r}
#| message: false
library(coorsim)
library(data.table)
```

Embeddings (Python) and LLM labels (Ollama) are precomputed, so only R is needed.

## Duration

Around 10 minutes.

## Social Science Usecase(s)

coorsim detects accounts that post semantically similar content within short
time frames, which can indicate coordinated social media manipulation
(Thiele et al., 2025). Unlike CooRTweet, which detects shared objects such as
URLs or hashtags (Righetti & Balluff, 2025), it compares the meaning of posts.

## Data

Toy data from the coorsim README: 100 posts by 10 accounts, of which
`coord_1` to `coord_5` post coordinated climate denial messages.

```{r}
tweets_df <- as.data.table(read.csv("data/toy_posts.csv", colClasses = "character"))
tweets_df[, created_at := as.POSIXct(created_at, format = "%Y-%m-%d %H:%M:%OS", tz = "UTC")]
users_df <- as.data.table(read.csv("data/toy_users.csv"))
head(tweets_df)
```

## Embeddings

Created with `save_embeddings()` and `Twitter/twhin-bert-base` (`scripts/make_embeddings.R`).

```{r}
emb_file <- "data/toy_sample_twhin-bert-base.h5"
```

## Similar posts

Post pairs within 180 seconds with a cosine similarity above 0.925.

```{r}
sim_dt <- detect_cosimilarity(
  data = tweets_df,
  embeddings = emb_file,
  time_window = 180,
  min_simil = 0.925,
  min_participation = 1,
  post_id = "post_id",
  account_id = "account_id",
  time = "created_at",
  content = "content",
  verbose = FALSE
)
head(sim_dt[, .(account_id, account_id_y, similarity, time_diff)])
```

## Communities

Accounts are linked by their similar posts and clustered into communities.

```{r}
coord <- coorsim_detect_groups(
  simdt = sim_dt,
  user_data = users_df,
  account_id = "account_id",
  verbose = FALSE
)
coord$node_list[, .(account_id, account_name, community)]
```

```{r}
#| fig-width: 12
#| fig-height: 10
#| warning: false
plot_communities(coord, palette_option = "D", start_color = .2, end_color = .8)
```

## LLM labels

Created with `scripts/make_labels.R`, which needs a local Ollama server:

```{r}
#| eval: false
coord <- sample_user_text(coord, sampling_ratio_posts = .33, sampling_ratio_users = .5)
coord <- label_users(coord, model = "llama3.1:8b")
coord <- label_communities(coord, model = "llama3.1:8b")
```

```{r}
#| eval: !expr file.exists("data/llm_labels.rds")
llm <- readRDS("data/llm_labels.rds")
stopifnot(identical(llm$node_list[order(account_id)]$community,
                    coord$node_list[order(account_id)]$community))
coord$user_labels <- llm$user_labels
coord$community_labels <- llm$community_labels
coord$community_labels[, .(community, label, description)]
```

```{r}
#| eval: !expr file.exists("data/llm_labels.rds")
#| fig-width: 12
#| fig-height: 10
#| warning: false
plot_communities(coord, palette_option = "D", start_color = .2, end_color = .8)
```

## Data quality

Share of flagged posts and accounts, to report alongside the dataset.

```{r}
data.table(
  level   = c("posts", "accounts"),
  flagged = c(uniqueN(coord$post_data$post_id), uniqueN(coord$node_list$account_id)),
  total   = c(nrow(tweets_df), nrow(users_df))
)[, share := round(flagged / total, 2)][]
```

## Conclusion

Now you know how to detect, describe and report coordinated posting with coorsim.

## References

- Righetti, N., & Balluff, P. (2025). CooRTweet: A generalized R software for
  coordinated network detection. *Computational Communication Research, 7*(1),
  1–23. https://doi.org/10.5117/CCR2025.1.7.RIGH
- Thiele, D. (2026). *coorsim* (R package version 0.0.8). https://github.com/thieled/coorsim
<!-- TODO: full reference for Thiele et al. (2025) -->
